Traffic Aware Resource Allocation Schemes for Multi-Cell \acs{MIMO}-\acs{OFDM} Systems

### 2016-02-08 Report/biography.tex
updated TSP submission

\begin{IEEEbiography}{Ganesh Venkatraman}
	(S'14) received the B.E. degree in electronics and communications engineering from the Madras University, Chennai, India in 2003, and the M.S. degree in electrical engineering from the Indian Institute of Technology (IIT) Madras, Chennai, India in 2006. He is currently pursuing the Dr. Sc. (Tech.) degree in the Department of Communication Engineering (DCE), Centre for Wireless Communications (CWC), University of Oulu, Oulu, Finland. %Prior to this, he worked as a Design Engineer in the Freescale Semiconductor India Pvt. Ltd., Noida, India during the year (2010-2011) and as a Research Engineer at the Center of Excellence in Wireless Technology (CEWiT), Chennai, India during the year (2008-2010). 
	His research interests include radio resource management, transceiver algorithms for wireless communications, and signal processing techniques in baseband implementation.
\end{IEEEbiography}

@@

\begin{IEEEbiography}[{\includegraphics[trim=0cm 0cm 0.5cm 0cm,clip,scale=0.094]{Nam_Tran.jpg}}]{Le-Nam Tran}
	(M'10) received the B.S. degree in electrical engineering from Ho Chi Minh City University of Technology, Ho Chi Minh City, Vietnam, in 2003 and the M.S. and Ph.D. degrees in radio engineering from Kyung Hee University, Seoul, Korea, in 2006 and 2009, respectively. In 2009, he joined the Department of Electrical Engineering, Kyung Hee University, as a Lecturer. From 2010 to 2014, he had held postdoctoral positions at the Signal Processing Laboratory, ACCESS Linnaeus Centre, KTH Royal Institute of Technology, Sweden and the Centre for Wireless Communications and the Department of Communications Engineering, University of Oulu, Finland. Since Sep. 2014, he has been a lecturer at the Department of Electronic Engineering, Maynooth University, Co. Kildare, Ireland. His current research interests include multiuser MIMO systems, energy-efficient communications, full-duplex transmission, and applications of optimization techniques.
\end{IEEEbiography}

>>>>

\begin{IEEEbiography}[{\includegraphics[trim=0cm 1.2cm 0.2cm 0.3cm,clip,scale=0.52]{TolliAntti_0.jpg}}]{Ganesh Venkatraman}
	(S'14) received the B.E. degree in electronics and communications engineering from the Madras University, Chennai, India in 2003, and the M.S. degree in electrical engineering from the Indian Institute of Technology (IIT) Madras, Chennai, India in 2006. He is currently pursuing the Dr. Sc. (Tech.) degree in the Department of Communication Engineering (DCE), Centre for Wireless Communications (CWC), University of Oulu, Oulu, Finland. Prior to this, he worked as a Design Engineer in the Freescale Semiconductor India Pvt. Ltd., Noida, India during the year (2010-2011) and as a Research Engineer at the Center of Excellence in Wireless Technology (CEWiT), Chennai, India during the year (2008-2010). His research interests include radio resource management, transceiver algorithms for wireless communications, and signal processing techniques in baseband implementation.
\end{IEEEbiography}

@@

\begin{IEEEbiography}[{\includegraphics[scale=0.094]{Nam_Tran.jpg}}]{Le-Nam Tran}
	(M'10) received the B.S. degree in electrical engineering from Ho Chi Minh City University of Technology, Ho Chi Minh City, Vietnam, in 2003 and the M.S. and Ph.D. degrees in radio engineering from Kyung Hee University, Seoul, Korea, in 2006 and 2009, respectively. In 2009, he joined the Department of Electrical Engineering, Kyung Hee University, as a Lecturer. From 2010 to 2014, he had held postdoctoral positions at the Signal Processing Laboratory, ACCESS Linnaeus Centre, KTH Royal Institute of Technology, Sweden and the Centre for Wireless Communications and the Department of Communications Engineering, University of Oulu, Finland. Since Sep. 2014, he has been a lecturer at the Department of Electronic Engineering, Maynooth University, Co. Kildare, Ireland. His current research interests include multiuser MIMO systems, energy-efficient communications, full-duplex transmission, and applications of optimization techniques.
\end{IEEEbiography}

### 2016-02-08 Report/manuscript.tex
after 3A + 1R
submitted
updated
updated TSP submission

\documentclass[10pt,journal,final,letterpaper]{./../Styles/IEEEtran}

\usepackage{amsmath,amssymb}
\usepackage{acronym,etoolbox}
\usepackage{graphicx,epstopdf}
\usepackage[ruled]{algorithm2e}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[subrefformat=parens,labelformat=parens,labelseparator=period,caption=false,font=footnotesize]{subfig}
\usepackage{multirow,cite,setspace,fixltx2e,lineno,verbatim,mathtools,url,cases}

\graphicspath{{./../Figures/}{./../Figures/Linux/}{./../Figures/Review/}}
\DeclareGraphicsExtensions{.eps}

@@

\bibliographystyle{./../Styles/IEEEtran}
\bibliography{./../Library/IEEEabrv,./../Library/kirja_survey}

>>>>

\documentclass[10pt,journal,final,letterpaper,twocolumn]{./../IEEE/IEEEtran/IEEEtran}

\usepackage{amsmath,amssymb}
\usepackage{acronym,etoolbox}
\usepackage{graphicx,epstopdf}
\usepackage[ruled]{algorithm2e}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[subrefformat=parens,labelformat=parens,labelseparator=period,caption=false,font=footnotesize]{subfig}
\usepackage{multirow,cite,setspace,fixltx2e,lineno,verbatim,mathtools,url,cases,algorithmic,placeins}

\graphicspath{{./../Figures/}{./../Figures/Linux/}{./../Figures/Review/}{./../Figures/Bio/}}
\DeclareGraphicsExtensions{.eps}

@@

\bibliographystyle{./../IEEE/IEEEtranBST/IEEEtran}
\bibliography{./../Library/IEEEabrv,./../Library/kirja_survey}

\input{biography}
